Verifying Demonstrations

### 2017-08-29 properties.tex
Removes transitive trust, excessive examples

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Transitive trust]
    \begin{itemize}
      \item Trusted journalist Jane attends to report.
      \item She witnesses Alice's proof.

@@

\begin{frame}
\begin{figure}
  \centering
  \mode<presentation>{%
    \only<1>{%
      \begin{tikzpicture}
        \tikzset{grow'=right,level distance=5em}
        \Tree [.Proof
        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ] [.tsig 
        {$t_s''$} ] ]
        {\dots}
        [.{wsig} {\dots} ]
        ]
      \end{tikzpicture}
    }
  }
  \only<2>{%
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} [.{osig} 
      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ] [.tsig 
      {$t_s''$} ] ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  }
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}

>>>>

\mode<none>{%
\begin{frame}
  \begin{idea}[Transitive trust]
    \begin{itemize}
      \item Trusted journalist Jane attends to report.
      \item She witnesses Alice's proof.

@@

\begin{frame}
\begin{figure}
  \centering
  \mode<presentation>{%
    \only<1>{%
      \begin{tikzpicture}
        \tikzset{grow'=right,level distance=5em}
        \Tree [.Proof
        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
        %[.tsig {$t_s''$} ]
        ]
        {\dots}
        [.{wsig} {\dots} ]
        ]
      \end{tikzpicture}
    }
  }
  \only<2>{%
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} [.{osig} 
      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
      %[.tsig {$t_s''$} ]
      ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  }
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}
